% ==============================================================================
% banq-bibliography.tex
% Consolidated bibliography for the unified XPower Banq bundle.
% Union of all bibitems from banq-pro, banq-apx, banq-lck, banq-log, with
% duplicates removed. Cross-document self-references (wp, apx, lck, log,
% mtp, sim, ref) are retained as ordinary entries so \cite calls resolve in
% bundle mode without requiring per-section labels.
%
% This file is \input{} from 006.banq-ref/banq-ref.tex (always — that subfile
% is the canonical home of both the standalone and bundle bibliographies).
% The other five children maintain their own \begin{thebibliography} blocks
% for standalone builds; those blocks are suppressed in bundle mode via
% \ifbundle, leaving banq-ref's input as the single bibliography.
% ==============================================================================

\begin{thebibliography}{99}

% --- XPower Banq companion documents (cross-references) ---

\bibitem{wp}
\textsc{Karun The Ritch}.
\newblock XPower Banq: A Permissionless DeFi Lending Protocol with Lethargic Governance and Beta-Distributed Position Caps.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

\bibitem{apx}
\textsc{Karun The Ritch}.
\newblock XPower Banq: Technical Appendices.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

\bibitem{lck}
\textsc{Karun The Ritch}.
\newblock XPower Banq: Ring-Buffer Time Locks.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

\bibitem{log}
\textsc{Karun The Ritch}.
\newblock XPower Banq: Log-Space Compounding Index.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

\bibitem{mtp}
\textsc{Karun The Ritch}.
\newblock XPower Banq: Mathematical Theory \& Proofs.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

\bibitem{sim}
\textsc{Karun The Ritch}.
\newblock XPower Banq: Simulations \& Risk Analysis.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

\bibitem{ref}
\textsc{Karun The Ritch}.
\newblock XPower Banq: References \& Glossary.
\newblock \emph{Preprint}, 2026.
\newblock \url{https://www.xpowerbanq.com}

% --- DeFi lending protocols ---

\bibitem{compound2019}
Leshner, R. and Hayes, G.
\newblock Compound: The Money Market Protocol.
\newblock \emph{Compound Whitepaper}, 2019.
\newblock \url{https://compound.finance/documents/Compound.Whitepaper.pdf}

\bibitem{aave2020}
Aave Protocol.
\newblock Aave Protocol Whitepaper V2.0.
\newblock \emph{Aave Documentation}, 2020.
\newblock \url{https://docs.aave.com/}

\bibitem{makerdao2017}
MakerDAO Team.
\newblock The Maker Protocol: MakerDAO's Multi-Collateral Dai (MCD) System.
\newblock \emph{MakerDAO Whitepaper}, 2017.
\newblock \url{https://makerdao.com/whitepaper/}

\bibitem{euler2022}
Euler Labs.
\newblock Euler Finance: Permissionless Lending Protocol.
\newblock \emph{Euler Whitepaper}, 2022.
\newblock \url{https://docs.euler.finance/}

\bibitem{liquity2021}
Lauko, R. and Pardoe, R.
\newblock Liquity: Decentralized Borrowing Protocol.
\newblock \emph{Liquity Whitepaper}, 2021.
\newblock \url{https://docs.liquity.org/}

\bibitem{morpho2022}
Frambot, P. and Gontier Delaunay, M.
\newblock Morpho Optimizer: Optimizing Decentralized Liquidity Protocols.
\newblock \emph{Morpho Whitepaper}, 2022.
\newblock \url{https://whitepaper.morpho.org/}

% --- Surveys and academic references ---

\bibitem{bartoletti2021}
Bartoletti, M., Chiang, J.H., and Lafuente, A.L.
\newblock SoK: Lending Pools in Decentralized Finance.
\newblock \emph{Financial Cryptography and Data Security (FC)}, LNCS vol.~12676, pp.~553--578, 2021.

\bibitem{werner2022}
Werner, S.M., Perez, D., Gudgeon, L., Klages-Mundt, A., Harz, D., and Knottenbelt, W.J.
\newblock SoK: Decentralized Finance (DeFi).
\newblock \emph{ACM Computing Surveys}, 2022.

\bibitem{gudgeon2020}
Gudgeon, L., Perez, D., Harz, D., Livshits, B., and Gervais, A.
\newblock The Decentralized Financial Crisis.
\newblock \emph{Crypto Valley Conference}, 2020.

\bibitem{perez2021}
Perez, D., Werner, S.M., Xu, J., and Livshits, B.
\newblock Liquidations: DeFi on a Knife-edge.
\newblock \emph{Financial Cryptography and Data Security}, 2021.

% --- Oracles and TWAPs ---

\bibitem{mackinga2022}
Mackinga, T., Nadahalli, T., and Wattenhofer, R.
\newblock TWAP Oracle Attacks: Easier Done than Said?
\newblock \emph{IEEE International Conference on Blockchain and Cryptocurrency}, 2022.

\bibitem{chainlink2017}
Ellis, S., Juels, A., and Nazarov, S.
\newblock ChainLink: A Decentralized Oracle Network.
\newblock \emph{Chainlink Whitepaper}, 2017.
\newblock \url{https://chain.link/whitepaper}

\bibitem{angeris2020}
Angeris, G. and Chitra, T.
\newblock Improved Price Oracles: Constant Function Market Makers.
\newblock \emph{ACM Conference on Advances in Financial Technologies (AFT)}, 2020.

\bibitem{uniswap2020}
Adams, H., Zinsmeister, N., and Robinson, D.
\newblock Uniswap v2 Core.
\newblock \emph{Uniswap Documentation}, 2020.
\newblock \url{https://docs.uniswap.org/}

\bibitem{uniswap2021}
Adams, H., Zinsmeister, N., Salem, M., Keefer, R., and Robinson, D.
\newblock Uniswap v3 Core.
\newblock \emph{Uniswap Documentation}, 2021.
\newblock \url{https://docs.uniswap.org/}

% --- MEV and attacks ---

\bibitem{daian2020}
Daian, P., Goldfeder, S., Kell, T., Li, Y., Zhao, X., Bentov, I., Breidenbach, L., and Juels, A.
\newblock Flash Boys 2.0: Frontrunning in Decentralized Exchanges, Miner Extractable Value, and Consensus Instability.
\newblock \emph{IEEE Symposium on Security and Privacy (S\&P)}, pp.~910--927, 2020.

\bibitem{qin2022}
Qin, K., Zhou, L., and Gervais, A.
\newblock Quantifying Blockchain Extractable Value: How dark is the forest?
\newblock \emph{IEEE Symposium on Security and Privacy (S\&P)}, pp.~198--214, 2022.

\bibitem{qin2021flashloans}
Qin, K., Zhou, L., Livshits, B., and Gervais, A.
\newblock Attacking the DeFi Ecosystem with Flash Loans for Fun and Profit.
\newblock \emph{Financial Cryptography and Data Security (FC)}, LNCS vol.~12674, pp.~3--32, 2021.

\bibitem{beanstalk2022}
Immunefi.
\newblock Hack Analysis: Beanstalk Governance Attack, April 2022.
\newblock \emph{Security Report}, 2022.
\newblock \url{https://medium.com/immunefi/hack-analysis-beanstalk-governance-attack-april-2022-f42788fc821e}

\bibitem{glassnode2020}
Glassnode Insights.
\newblock What Really Happened to MakerDAO on Black Thursday.
\newblock \emph{Glassnode Analysis}, March 2020.
\newblock \url{https://insights.glassnode.com/what-really-happened-to-makerdao/}

\bibitem{liu2023terra}
Liu, J., Makarov, I., and Schoar, A.
\newblock Anatomy of a Run: The Terra Luna Crash.
\newblock \emph{Harvard Law School Forum on Corporate Governance}, May 2023.
\newblock \url{https://corpgov.law.harvard.edu/2023/05/22/anatomy-of-a-run-the-terra-luna-crash/}

% --- Cryptography and Sybil ---

\bibitem{nakamoto2008}
Nakamoto, S.
\newblock Bitcoin: A Peer-to-Peer Electronic Cash System.
\newblock 2008.
\newblock \url{https://bitcoin.org/bitcoin.pdf}

\bibitem{douceur2002}
Douceur, J.R.
\newblock The Sybil Attack.
\newblock \emph{International Workshop on Peer-to-Peer Systems (IPTPS)}, LNCS vol.~2429, pp.~251--260, 2002.

\bibitem{dwork1992}
Dwork, C. and Naor, M.
\newblock Pricing via Processing or Combatting Junk Mail.
\newblock \emph{Advances in Cryptology -- CRYPTO '92}, LNCS vol.~740, pp.~139--147, 1992.

\bibitem{roughgarden2021}
Roughgarden, T.
\newblock Transaction Fee Mechanism Design.
\newblock \emph{ACM Conference on Economics and Computation (EC)}, 2021.

\bibitem{feist2019}
Feist, J., Grieco, G., and Groce, A.
\newblock Slither: A Static Analysis Framework for Smart Contracts.
\newblock \emph{IEEE/ACM International Workshop on Emerging Trends in Software Engineering for Blockchain (WETSEB)}, pp.~8--15, 2019.

% --- Vote-escrow and time-locks (banq-lck) ---

\bibitem{curve}
Curve Finance.
\newblock Vote-Escrowed CRV (veCRV).
\newblock \emph{Curve Documentation}, 2020.
\newblock \url{https://curve.readthedocs.io/dao-vecrv.html}

\bibitem{convex}
Convex Finance.
\newblock Vote-Locked CVX (vlCVX).
\newblock \emph{Convex Documentation}, 2021.
\newblock \url{https://docs.convexfinance.com/convexfinance/general-information/understanding-cvx/vote-locking}

\bibitem{oz-timelock}
OpenZeppelin.
\newblock TimelockController.
\newblock \emph{OpenZeppelin Contracts}, 2020.
\newblock \url{https://docs.openzeppelin.com/contracts/5.x/api/governance#TimelockController}

\bibitem{oz-math}
OpenZeppelin.
\newblock Math Library (mulDiv).
\newblock \emph{OpenZeppelin Contracts}, 2023.
\newblock \url{https://docs.openzeppelin.com/contracts/5.x/api/utils#Math}

\bibitem{openzeppelin2020}
OpenZeppelin Team.
\newblock OpenZeppelin Contracts.
\newblock \emph{OpenZeppelin Documentation}, 2020.
\newblock \url{https://docs.openzeppelin.com/contracts/}

\bibitem{debruijn}
de~Bruijn, N.G.
\newblock A combinatorial problem.
\newblock \emph{Proceedings of the Section of Sciences of the Koninklijke Nederlandse Akademie van Wetenschappen}, 49(7):758--764, 1946.

\bibitem{ring-buffer}
Lee, P.P.C., Bu, T., and Chandranmenon, G.P.
\newblock A lock-free, cache-efficient shared ring buffer for multi-core architectures.
\newblock In \emph{Proc.\ 5th ACM/IEEE Symposium on Architectures for Networking and Communications Systems (ANCS)}, pp.\ 78--79, 2009.
\newblock \url{https://doi.org/10.1145/1882486.1882508}

% --- Numerical methods (banq-log) ---

\bibitem{prbmath}
Razvan, P.
\newblock PRBMath: Solidity Library for Fixed-Point Arithmetic.
\newblock \emph{GitHub Repository}, 2023.
\newblock \url{https://github.com/PaulRBerg/prb-math}

\bibitem{higham2002}
Higham, N.J.
\newblock \emph{Accuracy and Stability of Numerical Algorithms}.
\newblock SIAM, 2nd edition, 2002.

\bibitem{blanchard2021}
Blanchard, P., Higham, D.J., and Higham, N.J.
\newblock Accurately Computing the Log-Sum-Exp and Softmax Functions.
\newblock \emph{IMA Journal of Numerical Analysis}, 41(4):2311--2330, 2021.
\newblock \url{https://doi.org/10.1093/imanum/draa038}

\bibitem{solidity2024}
Ethereum Foundation.
\newblock Solidity Documentation: Checked or Unchecked Arithmetic.
\newblock \emph{Solidity Docs}, v0.8.x, 2024.
\newblock \url{https://docs.soliditylang.org/en/latest/control-structures.html#checked-or-unchecked-arithmetic}

% --- Standards (EIP) ---

\bibitem{erc20}
Vogelsteller, F. and Buterin, V.
\newblock EIP-20: Token Standard.
\newblock \emph{Ethereum Improvement Proposals}, 2015.
\newblock \url{https://eips.ethereum.org/EIPS/eip-20}

\bibitem{erc4626}
Santoro, J., t11s, Jadeja, J., and Cuesta Ca\~{n}ada, A.
\newblock EIP-4626: Tokenized Vaults.
\newblock \emph{Ethereum Improvement Proposals}, 2022.
\newblock \url{https://eips.ethereum.org/EIPS/eip-4626}

% --- Finance and microstructure ---

\bibitem{kyle1985continuous}
Kyle, A.S.
\newblock Continuous Auctions and Insider Trading.
\newblock \emph{Econometrica}, 53(6):1315--1335, 1985.

\bibitem{merton1976}
Merton, R.C.
\newblock Option Pricing When Underlying Stock Returns Are Discontinuous.
\newblock \emph{Journal of Financial Economics}, 3(1--2):125--144, 1976.

\end{thebibliography}
